Genome-wide changes in expression during inflorescence architecture development

### 2015-08-26 ms.Rmd
MM

---
title: Genome-wide changes in expression during inflorescence architecture development
  in rice
csl: csl/the-plant-journal.csl
header-includes: \usepackage{graphicx}
output:
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    keep_md: yes
    number_sections: yes
    dev: "CairoPDF"
  word_document:
    fig_caption: yes
    reference_docx: csl/wordStyles.docx
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
bibliography: bib/test.bib
---

@@

(**our in situ results could go here or in SI**)

@@

**cluster y-axis of GSEA plot w/in protein type**

@@

There was an overrepresentation of MADS genes in **some clusters** and their overall expression is enriched in the spikelet meristem sample. These results correspond with previous studies that have established the importance of MADS genes in inflorescence development in rice and other plants (**expand**).

@@

>>>>

---
title: Genome-wide changes in expression during inflorescence architecture development
  in rice
csl: csl/the-plant-journal.csl
header-includes: \usepackage{graphicx}
output:
  word_document:
    fig_caption: yes
    reference_docx: csl/wordStyles.docx
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    keep_md: yes
    number_sections: yes
    dev: "CairoPDF"
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
bibliography: bib/test.bib
---

@@

**Our in situ results could go here or in SI**

@@

@@

There was an overrepresentation of MADS genes in clusters **xyz** and their overall expression is enriched in the spikelet meristem sample. These results correspond with previous studies that have established the importance of MADS genes in inflorescence development in rice and other plants (**expand**).

@@

## Plant material and sampling

*Oryza sativa* ssp. japonica cv. Nipponbare plants were grown in a growth chamber at 70% relative humidity at 30°C during the day and 26°C at night. After 7 weeks in long day conditions (LD; 14 hours light and 10 hours darkness) plants were transferred to short day conditions (SD; 10 hours light and 14 hours darkness) to induce floral transition. Inflorescence meristems were harvested from 6 to 14 days after the change of photoperiod **under which microscope?**.

## Tissue embedding, LASER microdissection and sequencing

Each inflorescence was harvested in 2 mL ice-cold 3:1 ethanol:acetic acid fixative solution, infiltrated **filtered?** twice under a mild vacuum for 15 minutes and stored for 20 hours in fresh fixative at 4°C. The following steps of tissue embedding for dissection were performed as described by @Mantegazza:2014di. Tissues were cut into 8 µm sections on an RM2155 or RM2255 microtome (Leica) and dissected on a LMD6000 or LMD7000 LASER dissector (Leica). RNA was amplified using the ARCTURUS PicoPure RNA Isolation Kit (ThermoFisher) and assayed on a 2100 Bioanalyzer with the RNA 6000 Pico Kit (Agilent) before amplification and cDNA synthesis with the Ovation RNA-Seq System V2 (NuGEN). Library preparation with **which kit** and 50-base single-end sequencing on the HiSeq 2000 platform (Illumina) were performed by IGA Technology Services (Udine, Italy).

## Data analyses

Analysis of the sequenced libraries was carried out with custom `bash`, `R` (**ref**) and `python` (**ref**) scripts. All of the code used for the analysis and to generate figures and tables for this report, along with the versions and paramaters of the software used, are available on GitHub (https://github.com/evoreprice/lmdPaper). Briefly, adaptor trimming was performed with `cutadapt` (**ref**) and reads were mapped to the MSUv7 genome (**ref**) using `rna-star` (**ref**) in 2-pass mode with annotations. Differential expression analysis to calculate L~2~FC values and transformed read counts was performed with the `DESeq2` package (**ref**).
